results notes

### 2022-09-02 RR_manuscript/results_notes.Rmd
♻️ - edit results section
♻️ - edit caveats

---
title: "results notes"
author: "Timo Roettger"
date: "2022-08-13"
output: html_document
---

@@

@@

>>>>

---
title: "results notes"
author: "Timo Roettger"
date: "2022-08-13"
output:
  html_document:
    number_sections: true
---

@@

## Between-team variability

<!-- TODO: discuss between-team variability -->

@@

<!-- Brainstorm of ideas -->

- Analytic flexibility applies to us (as principal investigators) too.
- Research question was vague enough to possibily inflate between-team variability (REF, Hannah Fraser; although it is a typical kind of question, as found in the literature). We do relate analytical flexibility with underspecified hypothesis in the previous section.
- This should be replicated with a different question/data set.
- With this study, we can suggest that at a minimum this is the between-team variability, but need more studies like this one.
- Generalisability to linguistics/language sciences tout-court is limited. Need to do same with other fields, like language development, historical data, sociolinguistics, etc.
- The focus is on quantitative data analysis, so that we expect the issues raised here to apply differently or not at all to qualitative data analysis.
- We have not investigated researcher positionality, which is known to be an important factor.
